netcdf_to_brick_projected

### 2018-10-23 src/help_extract_from_multiple_netCDFs.Rmd
html for slr

---
title: "help_extract_from_multiple_netCDFs"
author: "Samantha Andrews"
output: html_notebook
---

@@

# Package dependencies
You can install and load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first. If they are not installed, it will do so before loading
```{r pre-install packages, suppressMessages(expr)}
packages <- c("ncdf4", "sp") 
source("../src/ipak.R")
ipak(packages)
```

@@

```{r}
netcdf_list <- list.files("../data/env/netcdf", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/env/netcdf", pattern = '*.nc', full.names = FALSE) #false means the path is not included
library (ncdf4)
for (i in 1:no_netcdf) {
  print(netcdf_name[i]) #this just prings the name of the netCDF R is working on
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  temp_brick <- projectRaster(temp_brick, aea) #aea is an existing raster in the projection I want that I created (environmental_data_preperation)
  assign(netcdf_name[i], temp_brick) #this asigns the netCDF name to the raster brick
}
```

@@

`occurrence$id` (a unique observation ID)
`occurrence$decimalLongitude` (Longitude in decimal degree)
`occurrence$decimalLatitude` (Latitude in decimal degree)
`occurrence$dLongitudeM` (Longitude in meters)
`occurrence$LatitudeM` (Latitude in meters)
`occurrence$year` (year of observation)
`occurrence$month` (month of observation)
`occurrence$depthlayerno (depth of observation - the value corresponds to the depth layers in the raster bricks e.g. if `occurrence$depthlayerno` == `20`, then the observation is from the raster brick layer `[[20]]`)

@@

```{r}
occurrence <- read.csv("./data/bio/occurrence_help.csv", header = TRUE)
```

@@

```{r}
library(sp)
species_obs_date <- SpatialPointsDataFrame(coords = xy, data = data_aea, proj4string = CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")) #convert into a spatialpoints dataframe to do the extraction
species_obs_date <- spTransform(species_obs_date, CRS = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs") #need to reproject.... note -60 used to be -91. Changed to 'straighten up'
split_obs <- split(species_obs_date, paste(species_obs_date$year, species_obs_date$month))
```

>>>>

---
title: "help_extract_from_multiple_netCDFs"
author: "Samantha Andrews"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

@@

# Package dependencies
You can install and load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first. If they are not installed, it will do so before loading
```{r pre-install packages, suppressMessages(expr)}
packages <- c("ncdf4", "sp", "raster") 
source("../src/ipak.R")
ipak(packages)
```

@@

```{r}
aea <- raster("../output/env/aea.tif")
netcdf_list <- list.files("../data/env/netcdf", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/env/netcdf", pattern = '*.nc', full.names = FALSE) #false means the path is not included
library (ncdf4)
for (i in 1:no_netcdf) {
  print(netcdf_name[i]) #this just prings the name of the netCDF R is working on
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  temp_brick <- projectRaster(temp_brick, aea) #aea is an existing raster in the projection I want that I created (environmental_data_preperation)
  assign(netcdf_name[i], temp_brick) #this asigns the netCDF name to the raster brick
}
```

@@

`occurrence$id` (a unique observation ID)
`occurrence$decimalLongitude` (Longitude in decimal degree)
`occurrence$decimalLatitude` (Latitude in decimal degree)
`occurrence$dLongitudeM` (Longitude in meters)
`occurrence$LatitudeM` (Latitude in meters)
`occurrence$year` (year of observation)
`occurrence$month` (month of observation)
`occurrence$depthlayerno`  (depth of observation - the value corresponds to the depth layers in the raster bricks e.g. if `occurrence$depthlayerno`== `20`, then the observation is from the raster brick layer `[[20]]`)

@@

```{r}
occurrence <- read.csv("../data/bio/occurrence_help.csv", header = TRUE)
```

@@

```{r}
library(sp)
xy <- occurrence[ , c("decimalLongitude", "decimalLatitude")]
species_obs_date <- SpatialPointsDataFrame(coords = xy, data = occurrence, proj4string = CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")) #convert into a spatialpoints dataframe to do the extraction
species_obs_date <- spTransform(species_obs_date, CRS = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs") #need to reproject.... note -60 used to be -91. Changed to 'straighten up'
split_obs <- split(species_obs_date, paste(species_obs_date$year, species_obs_date$month))
```

### 2018-10-23 src/netcdf_to_brick_projected.Rmd
html for slr

maybe start by splitting the occurence data into year-month? Then you can search for the rasters without going through everything....
```{r}
library(sp)
species_obs_date <- SpatialPointsDataFrame(coords = xy, data = data_aea, proj4string = CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")) #convert into a spatialpoints dataframe to do the extraction
species_obs_date <- spTransform(species_obs_date, CRS = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs") #need to reproject.... note -60 used to be -91. Changed to 'straighten up'
split_obs <- split(species_obs_date, paste(species_obs_date$year, species_obs_date$month))
```

>>>>

maybe start by splitting the occurence data into year-month? Then you can search for the rasters without going through everything....
```{r}
library(sp)
xy <- data_aea[ , c("decimalLongitude", "decimalLatitude")]
species_obs_date <- SpatialPointsDataFrame(coords = xy, data = data_aea, proj4string = CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")) #convert into a spatialpoints dataframe to do the extraction
species_obs_date <- spTransform(species_obs_date, CRS = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs") #need to reproject.... note -60 used to be -91. Changed to 'straighten up'
split_obs <- split(species_obs_date, paste(species_obs_date$year, species_obs_date$month))
```
